The fundamental shape of dynamic experiences is preserved in episodic memory

### 2018-06-25 main.tex
added in last main text figure

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{figs/2_eventseg_v4.pdf}
\caption{\small \textbf{Modelling naturalistic stimuli and recall.} For all plots, darker colors indicate greater values and the range of each plot is 0-1.  A). A timepoints (1976) by topics (100) matrix representing the video stimulus.  Each row represents the most likely mixture of topics for a given timepoint. Each columns represents a different topic. B). A timepoints (1976) by topics (100) matrix representing participant \#13's recall. C). A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model. The white boxes represent `events' recovered by a hidden Markov model. D). A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13. E). An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  F). An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model. G. A recall events (27) by video events (34) correlation matrix for participant \#13. The yellow squares identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The yellow squares identify the video event with the highest correlation to a given average recall event.}
\label{fig:model}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/4_trajectory.pdf}
\caption{\small \textbf{Video and recall trajectory plots.} A). 2-dimensional embedding of recall events model. The arrows indicate the forward direction of the video events. B). 2-dimensional embedding of the average recall events.  The colors refer to the most similar video events.  The lines connecting the points represent the average probability of transitioning from one event to the other. The weight of the line is proportional to the transition probability.}
\label{fig:trajectory}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
\caption{\small \textbf{Modelling naturalistic stimuli and recall.} For all plots, darker colors indicate greater values and the range of each plot is 0-1.  A). A timepoints (1976) by topics (100) matrix representing the video stimulus.  Each row represents the most likely mixture of topics for a given timepoint. Each columns represents a different topic. B). A timepoints (1976) by topics (100) matrix representing participant \#13's recall. C). A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model. The white boxes represent `events' recovered by a hidden Markov model. D). A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13. E). An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  F). An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model. G. A recall events (27) by video events (34) correlation matrix for participant \#13. The yellow squares identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The yellow squares identify the video event with the highest correlation to a given average recall event.}
\label{fig:model}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/4_trajectory.pdf}
\caption{\small \textbf{Video and recall trajectory plots.} A). 2-dimensional embedding of video events model. The arrows indicate the forward direction of the video events. B). 2-dimensional embedding of the average recall events.  The colors refer to the most similar video events.  The lines connecting the points represent the average probability of transitioning from one event to the other. The opacity of the line is proportional to the transition probability (0 to 1). Arrows indicate the transition with the highest probability for each event.}
\label{fig:trajectory}
\end{figure}

@@

\begin{figure}[th!]
\centering
\includegraphics[width=1\textwidth]{figs/5_linesegs.pdf}
\caption{\small \textbf{Recall shape analysis and video/recall content.} A 2-dimensional embedding of the best fitting line segments model across all participant's recall event models.  The points outlined in black represent the ``hinge-points'' of the best fitting model colored according to their matching video event.  The points not outlined in black are individual participant recall events colored by the most similar video event. The kernel density plot represents the distribution across all points.  The word clouds for each event (left: video; right: recall) were created by taking the top 100 words for the topics that were ``activated'' during a particular event.}
\label{fig:linesegs}
\end{figure}
